---
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(readxl)
library(stringr)
library(dplyr)
library(tidyr)
library(tibble)
library(tidyverse)
library(kableExtra)
library(psych)
library(irr)
library(ggplot2)
library(data.table)
library(plyr)
library(lme4)
library(RColorBrewer)
library(corrplot)
library(ggcorrplot)
library(corrr)
library(lattice)
library(irrCAC)

options(digits = 4)
rm(list=ls())

colors = brewer.pal(n=8, name="Dark2")
colors_blue = c("#FFFFFF", "#D6EAF8", "#AED6F1", "#85C1E9", "#5DADE2", "#3498DB", "#2E86C1", "#2874A6", "#21618C", "#1B4F72")
```


```{r sample-lv-data, include = FALSE}
completed_scores <- list.files(path = "../ti_scoring_data/Completed Scores", pattern = "KPMP TI Descriptor Scoring")
study_ids <- str_sub(completed_scores, 1, 8)
scorer_ids <- str_sub(completed_scores, 43, 43)
scorer_ids <- str_replace(scorer_ids, ".xlsx", "")

tmp <- data.frame(
  file_id = completed_scores,
  study_id = study_ids,
  scorer_id = scorer_ids
)

df_smp = data.frame()

for(i in 1:length(completed_scores)){
  
  data <- read_xlsx(paste0("../ti_scoring_data/Completed Scores/", completed_scores[i]), skip = 3, col_names = TRUE)
  data <- data[, 1:(grep("END", names(data))[1]-1)]

  data_scores <- data[c(1, 3:(nrow(data)-1)), ] 

  data_scores <- data_scores %>%
    filter(rowSums(is.na(data_scores)) != (ncol(data_scores) - 1))
  data_scores[-1 , which(data_scores[1, ] == "No")] = NA
  data_scores <- data_scores[-1,]
  
  data_scores$prst <- apply(data_scores[,-1], 1, function(x) ifelse(sum(as.integer(x), na.rm = T) > 0, 1, 0))
  
  tmp <- data.frame(
    scorer_id = scorer_ids[i],
    study_id = study_ids[i]
      )
  tmp <- data.frame(tmp, data.frame(matrix(data_scores$prst, nrow = 1)))
  
  df_smp <- rbind(df_smp, tmp)
  
}
```

```{r sample-lv-score-data}
df_smp_long <- data.frame()

for(i in 3:44){

  score <- df_smp[, c(1:2, i)]
  score_df <- spread(score, key = scorer_id, value = names(score)[3])
  
  rownames(score_df) <- paste0(names(score)[3], score_df$study_id)
  tmp <- score_df[, -1]
  
  df_smp_long <- rbind(df_smp_long, tmp)
  
}
```


\clearpage

## ICC analysis

```{r}
score <- df_smp[, c(1:2, 3)]
score_df <- spread(score, key = scorer_id, value = names(score)[3])
  
rownames(score_df) <- score_df$study_id
score_df <- score_df[, -1]
```

The result of ICC analysis for Classic/Common-type descriptor is below:

```{r}
score_rst <- ICC(score_df, missing = FALSE, alpha = .05)
score_rst$results
```

The result of fitted random effects models is as follows:
```{r}
score_rst$summary
score_rst$lme
```

```{r icc-data, include=FALSE}
df_smp_icc <- data.frame()

for(i in 3:44){

  score <- df_smp[, c(1:2, i)]
  score_df <- spread(score, key = scorer_id, value = names(score)[3])
  
  rownames(score_df) <- score_df$study_id
  score_df <- score_df[, -1]
  
  score_rst <- ICC(score_df, missing = FALSE, alpha = .05)$results
  score_icc <- score_rst[score_rst$type == "ICC2", "ICC"]
  score_lb <- score_rst[score_rst$type == "ICC2", "lower bound"]
  score_ub <- score_rst[score_rst$type == "ICC2", "upper bound"]
  
  
  tmp <- data.frame(
    
    score_name = names(score)[3],
    icc = score_icc,
    icc_lb = score_lb,
    icc_ub = score_ub
    
  )
  
  df_smp_icc <- rbind(df_smp_icc, tmp)
  
}

df_smp_icc$Score <- factor(data_scores$`GRID COORDINATES`, levels=data_scores$`GRID COORDINATES`)
df_smp_icc$Domain <- c(rep("Renal Tubular Atrophy", 3), 
  rep("Tubular Cell Injury (other than atrophy)", 14), 
  rep("Tubulitis", 2),
  rep("Abnormal Tubular Luminal Morphology", 3),
  rep("Intratubular Casts", 10),
  rep("Tubular basement membrane Morphology", 2),
  rep("Extracellular matrix", 2),
  rep("Inflammation", 6))

df_smp_icc <- df_smp_icc %>%
  mutate(icc_group = ifelse(is.na(icc), "Unknown", ifelse(icc < 0.6, "<0.6", "0.6+")))
```

```{r figure2-icc-idv-all, fig.align='center', fig.cap='Estimated ICC of presence/abscence scoring of individual descriptors at the sample level with 95\\% CI.  A descriptor is counted as present if a reviewer called it present in any grid square, and absent if they said no for all grid squares. Marked NA when the features were never present in any of 9 samples.', fig.height=9, out.width='95%', warning = FALSE, message = FALSE}
ggplot(df_smp_icc, aes(x = Score, y = icc, fill = Domain)) + 
  geom_bar(stat = "identity") + coord_flip() + theme_bw() +
  scale_y_continuous(name = "ICC", breaks = c(0, 0.25, 0.5, 0.75, 0.9)) + scale_x_discrete(name = "Score") +
  scale_fill_manual(values = c('Renal Tubular Atrophy' = colors[1], 'Tubular Cell Injury (other than atrophy)' = colors[2],
                              'Tubulitis' = colors[3], 'Abnormal Tubular Luminal Morphology' = colors[4],
                              'Intratubular Casts' = colors[5], 'Tubular basement membrane Morphology' = colors[6],
                              'Extracellular matrix' = colors[7], 'Inflammation' = colors[8])) +
  theme(axis.title.x = element_text(size = 10), axis.title.y = element_text(size = 10), legend.position = "none") +
  geom_vline(xintercept = c(3.5, 17.5, 19.5, 22.5, 32.5, 34.5, 36.5), color = "black", linetype = 3, size = 1) +
  geom_hline(yintercept = c(0.5, 0.75, 0.9), linetype = 2, color = "red") +
  annotate("text", x = c(17, 19, 24, 31, 41, 42), y = -0.05, label = "NA", size = 3) +
  geom_errorbar(aes(ymin=icc_lb, ymax=icc_ub),
                  width=.2,                    # Width of the error bars
                  position=position_dodge(.9))
```

\clearpage

## Gwet AC

Description of function: [https://www.rdocumentation.org/packages/irrCAC/versions/1.0/topics/gwet.ac1.raw](https://www.rdocumentation.org/packages/irrCAC/versions/1.0/topics/gwet.ac1.raw)

```{r}
score <- df_smp[, c(1:2, 3)]
score_df <- spread(score, key = scorer_id, value = names(score)[3])
  
rownames(score_df) <- score_df$study_id
score_df <- score_df[, -1]
```

```{r echo=TRUE}
gwet.ac1.raw(score_df)
```

```{r ac-data, include=FALSE}
df_smp_ac <- data.frame()

for(i in 3:44){

  score <- df_smp[, c(1:2, i)]
  score_df <- spread(score, key = scorer_id, value = names(score)[3])
  
  rownames(score_df) <- score_df$study_id
  score_df <- score_df[, -1]
  
  score_rst <- gwet.ac1.raw(score_df)$est
  score_ac <- score_rst$coeff.val
  score_lb <- strsplit(score_rst$conf.int, ",")[[1]][1]
  score_lb <- as.numeric(str_replace(score_lb, "\\(", ""))
  score_ub <- strsplit(score_rst$conf.int, ",")[[1]][2]
  score_ub <- as.numeric(str_replace(score_ub, "\\)", ""))
  
  tmp <- data.frame(
    
    score_name = names(score)[3],
    ac = score_ac,
    ac_lb = score_lb,
    ac_ub = score_ub
    
  )
  
  df_smp_ac <- rbind(df_smp_ac, tmp)
  
}

df_smp_ac$Score <- factor(data_scores$`GRID COORDINATES`, levels=data_scores$`GRID COORDINATES`)
df_smp_ac$Domain <- c(rep("Renal Tubular Atrophy", 3), 
  rep("Tubular Cell Injury (other than atrophy)", 14), 
  rep("Tubulitis", 2),
  rep("Abnormal Tubular Luminal Morphology", 3),
  rep("Intratubular Casts", 10),
  rep("Tubular basement membrane Morphology", 2),
  rep("Extracellular matrix", 2),
  rep("Inflammation", 6))

df_smp_ac <- df_smp_ac %>%
  mutate(ac_group = ifelse(ac < 0.4, "<0.4", ifelse(ac < 0.6, "0.4-<0.6", "0.6+")))

df_smp_grouped <- cbind(df_smp_ac, df_smp_icc$icc, df_smp_icc$icc_group)
df_smp_grouped <- df_smp_grouped %>%
  mutate(group = ifelse(df_smp_icc$icc_group == "Unknown", "Unknown", 
                        ifelse(ac_group == "<0.4", "Very Problematic", 
                               ifelse(ac_group == "0.4-<0.6", "Problematic", 
                                      ifelse(df_smp_icc$icc_group == "<0.6", "Possibly Problematic", "Reasonable")))))
```

```{r figure2-ac-idv-all, fig.align='center', fig.cap='Estimated Gwet AC1 of individual descriptors with 95\\% CI. No CI was presented when there is no variation.', fig.height=9, out.width='95%', warning = FALSE, message = FALSE}
ggplot(df_smp_ac, aes(x = Score, y = ac, fill = Domain)) + 
  geom_bar(stat = "identity") + coord_flip() + theme_bw() +
  scale_y_continuous(name = "ac") + scale_x_discrete(name = "Score") +
  scale_fill_manual(values = c('Renal Tubular Atrophy' = colors[1], 'Tubular Cell Injury (other than atrophy)' = colors[2],
                              'Tubulitis' = colors[3], 'Abnormal Tubular Luminal Morphology' = colors[4],
                              'Intratubular Casts' = colors[5], 'Tubular basement membrane Morphology' = colors[6],
                              'Extracellular matrix' = colors[7], 'Inflammation' = colors[8])) +
  theme(axis.title.x = element_text(size = 10), axis.title.y = element_text(size = 10), legend.position = "none") +
  geom_vline(xintercept = c(3.5, 17.5, 19.5, 22.5, 32.5, 34.5, 36.5), color = "black", linetype = 3, size = 1) +
# geom_hline(yintercept = c(0.5, 0.75, 0.9), linetype = 2, color = "red") +
# annotate("text", x = c(17, 19, 24, 31, 41, 42), y = -0.05, label = "NA", size = 3) +
  geom_errorbar(aes(ymin=ac_lb, ymax=ac_ub),
                  width=.2,                    # Width of the error bars
                  position=position_dodge(.9))
```


\clearpage

# Supplementary material
## Scoring

In the above analyses, presence scoring of each descriptor is as follows. A descriptor is counted as present if a reviewer called it present in any grid square, and absent if they said no for all grid squares.

\clearpage

```{r}
score_list <- list()

for (i in 3:44){
  score <- df_smp[, c(1:2, i)]
  score_df <- spread(score, key = scorer_id, value = names(score)[3])
  
  rownames(score_df) <- score_df$study_id
  score_df <- score_df[, -1]

  score_df <- score_df[c("27-10089", "30-11033", "31-10063",
                         "29-10012", "30-10125", "32-10296", 
                         "28-10051", "29-10395", "34-10184"),]
  
  score_list[[i-2]] <- score_df
}

kb_score_tb <- function(x){
  return(kable(score_list[[x]], booktabs = TRUE, align = "c", linesep = "", caption = paste0(data_scores$`GRID COORDINATES`[x]))) %>%
    kable_styling(latex_options = c("HOLD_position"))

  }
```

```{r}
very_prob <- df_smp[,c(1:2, which(df_smp_grouped$group == "Very Problematic") + 2)]
very_prob_score <- df_smp_grouped %>% filter(group == "Very Problematic")
```

```{r eval=FALSE}
x5 <- very_prob[, c(1:3)]
x5$study_id <- factor(x5$study_id, levels = c("27-10089", "30-11033", "31-10063",
                                              "29-10012", "30-10125", "32-10296", 
                                              "28-10051", "29-10395", "34-10184"), labels = c("Sample 1","Sample 2","Sample 3",
                                                                                              "Sample 4","Sample 5","Sample 6",
                                                                                              "Sample 7","Sample 8","Sample 9"))
x5_df <- spread(x5, key = scorer_id, value = X5)

rownames(x5_df) <- x5_df$study_id
x5_df <- x5_df[, -1]

x5$study_id <- fct_rev(x5$study_id)
ggplot(x5, aes(x = study_id, y = X5, color = scorer_id)) +
  geom_jitter(size = 2.5, height = .1, width = 0, alpha = 0.8) + coord_flip() +
  ylab("Presence(1) or Absence(0) Score") +
  scale_y_continuous(breaks = c(0, 1)) + 
  theme_bw() + xlab("Sample") + labs(color = "Scorer") +
  geom_vline(xintercept = c(3.5, 6.5)) +
  theme(axis.title.y = element_blank()) +
  labs(title = very_prob_score$Score[1], subtitle = paste0("Domain: ", very_prob_score$Domain[1]))
```

```{r out.width='95%', fig.align='center', fig.height = 4}
figure_list <- list()

for(i in 1:nrow(very_prob_score)){
  x <- very_prob[, c(1:2, i+2)]
  x$study_id <- factor(x$study_id, levels = c("27-10089", "30-11033", "31-10063",
                                              "29-10012", "30-10125", "32-10296", 
                                              "28-10051", "29-10395", "34-10184"), 
                       labels = c("Sample 1","Sample 2","Sample 3",
                                  "Sample 4","Sample 5","Sample 6",
                                  "Sample 7","Sample 8","Sample 9"))
  
  x$study_id <- fct_rev(x$study_id)
  names(x) <- c(names(x)[1:2], "x")
  figure_list[[i]] <- ggplot(x, aes(x = study_id, y = x, color = scorer_id)) +
    geom_jitter(size = 2.5, height = .1, width = 0, alpha = 0.8) + coord_flip() +
    ylab("Presence(1) or Absence(0) Score") +
    scale_y_continuous(breaks = c(0, 1)) + 
    theme_bw() + xlab("Sample") + labs(color = "Scorer") +
    geom_vline(xintercept = c(3.5, 6.5)) +
    theme(axis.title.y = element_blank()) +
    labs(title = very_prob_score$Score[i], subtitle = paste0("Domain: ", very_prob_score$Domain[i]))
}

figure_list[[1]]
figure_list[[2]]
figure_list[[3]]
figure_list[[4]]
figure_list[[5]]
figure_list[[6]]
figure_list[[7]]
figure_list[[8]]
# trellis.device(windows, height=6, width=10)
```

<!-- ```{r} -->
<!-- score <- df_smp[, c(1:2, 3)] -->
<!-- score_df <- spread(score, key = scorer_id, value = names(score)[3]) -->

<!-- rownames(score_df) <- score_df$study_id -->
<!-- score_df <- score_df[, -1] -->

<!-- kable(score_df, booktabs = TRUE, align = "c", linesep = "", caption = "Presence scoring of Classic/Common-type. A descriptor is counted as present if a reviewer called it present in any grid square, and absent if they said no for all grid squares.") %>% -->
<!--   kable_styling(latex_options = c("HOLD_position")) -->
<!-- ``` -->

```{r eval=FALSE, fig.pos='H', include=FALSE}
kb_score_tb(1)
kb_score_tb(2)
kb_score_tb(3)
kb_score_tb(4)
kb_score_tb(5)
kb_score_tb(6)
kb_score_tb(7)
kb_score_tb(8)
kb_score_tb(9)
kb_score_tb(10)
kb_score_tb(11)
kb_score_tb(12)
kb_score_tb(13)
kb_score_tb(14)
kb_score_tb(15)
kb_score_tb(16)
kb_score_tb(17)
kb_score_tb(18)
kb_score_tb(19)
kb_score_tb(20)
kb_score_tb(21)
kb_score_tb(22)
kb_score_tb(23)
kb_score_tb(24)
kb_score_tb(25)
kb_score_tb(26)
kb_score_tb(27)
kb_score_tb(28)
kb_score_tb(29)
kb_score_tb(30)
kb_score_tb(31)
kb_score_tb(32)
kb_score_tb(33)
kb_score_tb(34)
kb_score_tb(35)
kb_score_tb(36)
kb_score_tb(37)
kb_score_tb(38)
kb_score_tb(39)
kb_score_tb(40)
kb_score_tb(41)
kb_score_tb(42)
```
